Jager: Symbolic Specification-Based Program Adjustment

### 2013-04-30 paper/paper.tex
Removing the empty background section until it makes sense to actually add it back in. We'll need content for that to happen.
Updating the author part of the title to include more information.
Adding a bunch of content to the Fault Localization section.

\author{Joshua Branchaud \and Eric Rizzi}
\date{}

@@

\subsection{Background}

@@

>>>>

\author{Joshua Branchaud and Eric Rizzi \\
Department of Computer Science and Engineering \\
University of Nebraska-Lincoln \\
\{jbrancha,erizzi\}@cse.unl.edu}
\date{}

@@

% We need to think about how we are going to provide a background for the
% work, but right now an explicit background section isn't fitting. It may
% work its way in later though.
%\subsection{Background}

@@

As discussed earlier in the limitations, it is important to isolate a very
small portion of the program that can be blamed for the fault. This is where
fault localization comes into the picture. In our case, we are interested in
identifying a single statement that is potentially faulty. It is that faulty
statement that we attempt to adjust in such a way that \emph{fixes} the
program. Like SemFix \cite{}, we borrow from the approach of Jones et al.
\cite{JonesTarantula} by computing a ranked list of \emph{suspicious}
statements. Unlike Jones et al. and SemFix though, we do not use traces from
the runs of test cases in a test suite. Instead, we utilize the traces
produced by symbolic execution.

The approach for localizing faults is to build a ranked list of the most
supsicious statements in the program. We present the suspiciousness formula
used for this kind of fault localization in Equation~\ref{tarantula1}.

\begin{equation}
\label{tarantula1}
    susp(s) = \frac{failing(s)/totalFailing}{failing(s)/totalFailing + passing(s)/totalPassing}
\end{equation}

Equation~\ref{tarantula1} relies entirely on the presence of a test suite
that can be run to differentiate between passing and failing test cases
which refer to concrete traces. It also relies on the test suite being of a
certain quality with the suite having as high of a coverage metric as
possible. Unlike these approaches, our approach uses \emph{good} and
\emph{bad} symbolic traces (discussed in the previous section) to replace
the passing and failing concrete traces. Thus, we present a subtle variant
of the suspiciousness formula with Equation~\ref{tarantula2}.

\begin{equation}
\label{tarantula2}
    susp(s) = \frac{bad(s)/totalBad}{bad(s)/totalBad + good(s)/totalGood}
\end{equation}

By using Equation~\ref{tarantula2} with all the traces through the program, we can
quickly compute a list of statements ranked by suspiciousness. Instead of
being tied to a test suite, the suspiciousness is based on all traces
through the program and their ability to meet (or not) the specifications of
the program. We believe this provides a fuller, more precise picture of what
statements may be culpable. However, we do recognize that just as test
suites can have low coverage, the specifications for the program may not be
strong enough to say much.

Once we have a ranked list of suspicious statements, we can grab the most
suspicious statement and pass it to the next phases of our technique so that
an adjustment can be made. If there are multiple statements with the same
suspiciousness score, we arbitrarily pick one. If a statement doesn't match
the kind of statements we attempt to repair, then we grab the next statement
that does fall in line. This is necessary as long as we have a limited
repair grammar. Additionally, if a suitable repair can not be found for the
first statement passed along, then we pass along a subsequent statement.
